---
---

## Exercises

### Exercise 1

Now that you've learned a bit about extracting strings, try using regex to extract 
money values from the e-mail body content. 

### Exercise 2

We plotted the number of characters in each word above.  Word frequency in a document-term matrix might also be interesting. Try plotting a histogram of the number of times a word appears. 

### Exercise 3

What terms are associated with the word pipeline ("pipelin" after trimming)?  How might you visualize this? 


## Solutions

```{r, include=FALSE}
library(stringr)
library(tm)
library(ggplot2)  
```

### Solution 1

```{r, title = "Solution"}
str_extract_all(content(email), '\\$\\S+\\b') 
```

### Solution 2

```{r, title = "Solution"}
ggplot(words, aes(x = total)) +
       geom_histogram(binwidth = 1)
```

The frequency of some words isn't very informative.  You can filter by term or by total number of occurrences. 

```{r, title = "Solution"}
words_trim <- filter(words, total < 250)
         
ggplot(words_trim, aes(x = total)) +
       geom_histogram(binwidth = 1)
```

### Solution 3

```{r, title = "Solution"}
word_assoc <- findAssocs(dtm_trimmed, 'pipelin', 0.6)

word_assoc <- data.frame(word = names(word_assoc[[1]]),
                         assoc = word_assoc,
                         row.names = NULL)
```

```{r, title = "Solution"}
ggplot(word_assoc, aes(label = word, size = pipelin)) +
       geom_text_wordcloud_area()
```

